Paper 2: Vitamin D

### 2017-11-08 doc/vitaminD.Rmd
explorary analysis with eGFR and uVDBP versus uVDBP:creatinine

# Clean data
vitd <- ds %>% 
  filter(fVN == "Baseline") %>% 
  select(vitdStatus, udbpCr) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot_slides("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:Creatinine (μg/mmol)")

>>>>

# Clean data
vitd <- ds %>% 
  filter(fVN == "Baseline") %>% 
  select(vitdStatus, udbpCr, UDBP) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(UDBP)", 
            "Vitamin D Status",
            "log uVDBP (μg/mmol)")
